```{r}
cat("\014")
rm(list = ls())
```

## working directory check

```{r}
getwd()

```
# set the working directory

```{r}
setwd("D:/R-code")
```

```{r}
pacman::p_load(pacman,caTools,party,partykit,
               rpart,psych,caret,ROCR,caret,ISLR,Metrics,
               BiocManager,dplyr,rio)
```

## importing dataset

```{r}
df <- import("mushrooms.csv")
glimpse(df)
```


```{r}
head(df)
```


```{r}
dim(df)
```

```{r}
colSums(is.na(df))
```
```{r}
char_col = names(select_if(df, is.character))
for (col in char_col)
{
  df[,col]=as.factor(df[,col])
}
head(df)
str(df)
```


## psych library is used to check normality and perform correlograms

```{r}
describe(df)
```

## model selection
```{r}
#iris
set.seed(5)
split=sample.split(df,SplitRatio = 0.8)
Train=subset(df,split=="TRUE")
Test=subset(df,split=="FALSE")

```


```{r}
tree<-ctree(class~.,data = Train)
tree
```
##Plots Using Ctree
```{r}
ct <- ctree(class~ ., data = Train, maxdepth = 5, alpha = 0.5)
st <- as.simpleparty(ct)
plot(st)
```
```{r}
y_pred=predict(tree,Test,type="response")
head(y_pred)

```
## To predict the class using rpart () function for the class method. rpart () uses the Gini index measure to split the nodes.
```{r}
library(rpart)
tr<-rpart(class~., Train)
library (rpart.plot)
rpart.plot(tr)
```

##From the decision tree shown above we can conclude that anyone whose odor =a,l,n and spore-print-color in b, h, k, n, o, u, w, y is edible and  remaining poisonous mushroom.

```{r}
unique(df$class)
```

```{r}
cm=table(Predicted=y_pred,actual=Test$class)
cm
```

```{r}
accuracy=sum(diag(cm))/sum(cm)
accuracy
```

```{r}
caret::confusionMatrix(Test$class,y_pred)
```
```{r}
actual=ifelse(Test$class=="e",0,1)
head(actual)
predicted=ifelse(y_pred=="e",0,1)
head(predicted)
```

```{r}

ROCR_pred=prediction(actual,predicted)
performance_ROC=performance(ROCR_pred,'tpr','fpr')
```

```{r}
plot(performance_ROC,colorize=TRUE)
```

```{r}
#find optimal cutoff probability to use to maximize accuracy
optimal <- optimalCutoff(actual, predicted)
optimal
```



```{r}
InformationValue::confusionMatrix(actual,predicted>optimal)
```

```{r}
#convert defaults from "Yes" and "No" to 1's and 0's
pred <- ifelse(predicted>optimal,1,0)
```

## accuracy using library
```{r}
pred=ifelse(predicted>optimal,1,0)
accuracy(actual,pred)
```
```{r}
#calculate sensitivity
sensitivity(actual,pred)
```


