```{r}
cat("\014")
rm(list = ls())
```

## working directory check

```{r}
getwd()

```
# set the working directory

```{r}
setwd("D:/R-code")
```

# load necessary library
```{r}
pacman::p_load(pacman,caTools,party,partykit,rpart)
```

## model selection
```{r}
#iris
set.seed(5)
split=sample.split(iris,SplitRatio = 0.8)
Train=subset(iris,split=="TRUE")
Test=subset(iris,split=="FALSE")

```


##Creating a model to predict high, low, medium among the inputs using rparty
```{r}
tree<-ctree(Species~.,data = Train)
tree
```
##Plots Using Ctree
```{r}
ct <- ctree(Species~ ., data = Train, maxdepth = 5, alpha = 0.5)
st <- as.simpleparty(ct)
plot(st)
```

```{r}
y_pred=predict(tree,Test,type="prob")
y_pred
```



## To predict the class using rpart () function for the class method. rpart () uses the Gini index measure to split the nodes.
```{r}
library(rpart)
tr<-rpart(Species~., Train)
library (rpart.plot)
rpart.plot(tr)
```

##From the decision tree shown above we can conclude that anyone whose Petal.Length < 2.5 is setosa and Petal.Length < 4.9 is a versicolor and remaining virginica.