```{r}
cat("\014")
rm(list = ls())
```

## working directory check

```{r}
getwd()

```
# set the working directory

```{r}
setwd("D:/R-code")
```

```{r}
pacman::p_load(pacman,caTools,party,partykit,
               rpart,psych,caret,ROCR,caret,ISLR,Metrics,
               BiocManager,dplyr,rio,randomForest)
```

## importing dataset

```{r}
df <- import("train.csv")
glimpse(df)
```
```{r}
head(df)
```
```{r}
dim(df)
```

```{r}
colSums(is.na(df))
```

## psych library is used to check normality and perform correlograms

```{r}
describe(df)
```
## model selection
```{r}
#iris
set.seed(5)
split=sample.split(df,SplitRatio = 0.8)
Train=subset(df,split=="TRUE")
Test=subset(df,split=="FALSE")
Train$price_range <- as.character(Train$price_range)
Train$price_range <- as.factor(Train$price_range)
```

```{r}
forest <- randomForest(price_range~.,data = Train)
forest
```
```{r}
Test$price_range <- as.character(Test$price_range)
Test$price_range <- as.factor(Test$price_range)
y_pred=predict(forest,Test,type="response")
head(y_pred)

```




##Plots Using randomforest
```{r}
rft <- randomForest(price_range~ ., data = Train, maxdepth = 5, alpha = 0.5)
plot(rft)
```

```{r}
out.importance <- round(importance(forest), 2)
out.importance
```
## From the random forest shown above we can conclude that the battery_power  score are the important factors deciding Price_range type. Also the model has only 7.5% error which means we can predict with 93.5% accuracy.


```{r}
cm=table(Predicted=y_pred,actual=Test$price_range)
cm
```

```{r}
caret::confusionMatrix(Test$price_range,y_pred)
```

```{r}
cat("\014")
rm(list = ls())
```


