```{r}
cat("\014")
rm(list = ls())
```

## working directory check

```{r}
getwd()

```
# set the working directory

```{r}
setwd("D:/R-code")
```

# load necessary library
```{r}
pacman::p_load(pacman,lares,beepr)
```

## The data we'll use is the Titanic dataset
```{r}
data(dft)
df <- subset(dft, select = -c(Ticket, PassengerId, Cabin))
```

##Classification: Binary
Let's begin with a binary (TRUE/FALSE) model to predict if each passenger Survived
```{r}
r <- h2o_automl(df, y = Survived, max_models = 1, impute = FALSE, target = "TRUE")
```
```{r}
plot(r)
```
```{r}
r$metrics
```
```{r}
r$plots$metrics
```

```{r}
head(r$importance)
```
```{r}
r$plots$importance
```

##Classification: Multi-Categorical
Now, let's run a multi-categorical (+2 labels) model to predict Pclass of each passenger
```{r}
r <- h2o_automl(df, Pclass, ignore = c("Fare", "Cabin"), max_time = 30, plots = FALSE)
```
```{r}
plot(r)
```
##Regression
Finally, a regression model with continuous values to predict Fare payed by passenger
```{r}
r <- h2o_automl(df, y = "Fare", ignore = "Pclass", exclude_algos = NULL, quiet = TRUE)
print(r)
```
```{r}
plot(r)
```























