```{r}
cat("\014")
rm(list = ls())
```

## working directory check

```{r}
getwd()

```
# set the working directory

```{r}
setwd("D:/R-code")
```

# load necessary library
```{r}
pacman::p_load(pacman,factoextra,cluster)
```


# load data
```{r}
df <- USArrests
```

# remove rows with missing values
```{r}
df <- na.omit(df)
```

# scale each variable to have a mean of 0 and sd of 1
```{r}
df <- scale(df)
```

# view first six rows of dataset
```{r}
head(df)
```
To perform hierarchical clustering in R we can use the agnes() function from the cluster package

# define linkage methods
```{r}
m <- c( "average", "single", "complete", "ward")
names(m) <- c( "average", "single", "complete", "ward")
```

#function to compute agglomerative coefficient
```{r}
ac <- function(x) {
  agnes(df, method = x)$ac
}
```

#calculate agglomerative coefficient for each clustering linkage method
```{r}
sapply(m, ac)
```
# perform hierarchical clustering using Ward's minimum variance
```{r}
clust <- agnes(df, method = "ward")
```


# produce dendrogram

```{r}
pltree(clust, cex = 0.6, hang = -1, main = "Dendrogram") 
```
To Determine the Optimal Number of Clusters

# calculate gap statistic for each number of clusters (up to 10 clusters)
```{r}
gap_stat <- clusGap(df, FUN = hcut, nstart = 25, K.max = 10, B = 50)
```
# produce plot of clusters vs. gap statistic
```{r}
fviz_gap_stat(gap_stat)
```
From the plot we can see that the gap statistic is highest at k = 4 clusters. Thus, we’ll choose to group our observations into 4 distinct clusters.

Applying Cluster Labels to Original Dataset
#compute distance matrix
```{r}
d <- dist(df, method = "euclidean")
```

#perform hierarchical clustering using Ward's method
```{r}
final_clust <- hclust(d, method = "ward.D2" )
```

#cut the dendrogram into 4 clusters
```{r}
groups <- cutree(final_clust, k=4)
```

#find number of observations in each cluster
```{r}
table(groups)
```

#append cluster labels to original data
```{r}
final_data <- cbind(USArrests, cluster = groups)
```

#display first six rows of final data
```{r}
head(final_data)
```


#find mean values for each cluster
```{r}
aggregate(final_data, by=list(cluster=final_data$cluster), mean)
```
We interpret this output is as follows:

1.The mean number of murders per 100,000 citizens among the states in cluster 1 is 14.67.
2.The mean number of assaults per 100,000 citizens among the states in cluster 1 is 251.28.
3.The mean percentage of residents living in an urban area among the states in cluster 1 is   54.28%.
4.The mean number of rapes per 100,000 citizens among the states in cluster 1 is 21.68.


```{r}
cat("\014")
rm(list = ls())
```































